### 2021-06-07 thesis/tex/DCtheory.tex
update

We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
\section{PINGU}
The methodology behind the PINGU simulations are the same as with our DeepCore study~. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
As with the DeepCore data, the PINGU Monte Carlo is divided into eight 
$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
We generate "data" by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.

>>>>

\section{PINGU}
The methodology behind the PINGU simulations are the same as with our DeepCore study~. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
As with the DeepCore data, the PINGU Monte Carlo is divided into eight 
$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.

### 2021-06-07 thesis/tex/SM.tex
update

Together, these groups make up the local symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
This symmetry group determines the form of the three coupling constants of nature, whose numerical values must be experimentally measured. 
Since the vector bosons are represented by the generators, they are wholly constrained by the symmetry group. However, the scalar bosons\footnote{The Standard Model only has one scalar boson: the Higgs boson.} and fermions are free as long as they
belong to representations of the symmetry group. By this construction, the fermions have more degrees of freedom with which we can propose amendments to the model with. Even the
number of fermions must be experimentally derived. In this work,
we will use this leniency to make drastic modifications to the Standard Model fermions and examine to which extent these theories might be falsifiable.

\subsection{Lepton mixing}
In this section, we will see how the neutral leptons -- the neutrinos -- interact with the charged leptons, 
which is the first stepping stone in our journey.

In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
\begin{align}
    \label{eq:YukawaLagrangian}
    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime}
\end{align}
has a non-diagonal Yukawa coupling matrix $Y^{\prime \ell}$, which results in the charged lepton masses being non-definite. This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$
\begin{align}\label{eq:leptonYukawaDiag}
    V_{L}^{\ell \dagger} Y^{\prime \ell} V_{R}^{\ell}=Y^{\ell}\,.
\end{align}
This procedure give the charged lepton fields $\ell_{X}=V_{X}^{\ell \dagger} \ell_{X}^{\prime}$ definite mass. 
However, this alters the form of the neutral and charged current interactions, which the neutrinos undergo. The leptonic charged weak current now takes the form
\begin{align}
    \label{eq:j_CC}
    j^\rho_W &= 2 \bar{\nu}^\prime_\alpha \gamma^\rho \ell^\prime_\alpha \nonumber \\
             &= 2 \bar{\nu}_\alpha V^{\ell \dagger} \gamma^\rho V^\ell \ell_\alpha \nonumber \\
             &= 2 \bar{\nu}_\alpha \gamma^\rho \ell_\alpha\,,
\end{align}
where each lepton field and matrix have an implied $L$ subscript, which was dropped for clarity. The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$. However, 
$\nu_\alpha$ remained massless, since no flavor rotation $V^{\ell \dagger}$ can make massless fields massive. In the next section,
we shall make our first extension of the Standard Model, by introducing neutrino masses.
%TODO:more here about SM and lepton mixing? maybe about mass/massless particles. why does SM predict massless neutrinos, and 
%what implications does it have?
% \bibliographystyle{apalike}
% \bibliography{ref}
% \end{document}

>>>>

Together, these groups make up the local (gauge) symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
This symmetry group determines the form of the three coupling constants of nature, whose numerical values must be experimentally measured. 
Since the vector bosons are represented by the generators, they are wholly constrained by the symmetry group. However, the scalar bosons and fermions are free as long as they
belong to representations of the symmetry group. By this construction, the fermions have more degrees of freedom with which we can propose amendments to the model with. Even the
number of fermions must be experimentally derived. In this work,
we will use this leniency to make drastic modifications to the Standard Model fermions and examine to which extent these theories might be falsifiable.

\subsection{Lepton mixing}
Now we shall see how the charged leptons interact with the chargeless neutrinos.
Consider how charged leptons interact with the Higgs field. In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
\begin{align}
    \label{eq:YukawaLagrangian}
    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime}
\end{align}
has a non-diagonal Yukawa coupling matrix $Y^{\prime \ell}$, which results in the charged lepton masses being non-definite. This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$
\begin{align}\label{eq:leptonYukawaDiag}
    V_{L}^{\ell \dagger} Y^{\prime \ell} V_{R}^{\ell}=Y^{\ell}\,.
\end{align}
This procedure give the charged lepton fields $\ell_{X}=V_{X}^{\ell \dagger} \ell_{X}^{\prime}$ definite mass. 
However, this alters the form of the neutral and charged current interactions, which the neutrinos undergo. The leptonic charged weak current now takes the form
\begin{align}
    \label{eq:j_CC}
    j^\rho_W &= 2 \bar{\nu}^\prime_\alpha \gamma^\rho \ell^\prime_\alpha \nonumber \\
             &= 2 \bar{\nu}_\alpha V^{\ell \dagger} \gamma^\rho V^\ell \ell_\alpha \nonumber \\
             &= 2 \bar{\nu}_\alpha \gamma^\rho \ell_\alpha\,,
\end{align}
where each lepton field and matrix have an implied $L$ subscript, which was dropped for clarity. The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$. However, 
$\nu_\alpha$ remained massless, since no flavor rotation $V^{\ell \dagger}$ can make massless fields massive.
%TODO:more here about SM and lepton mixing? maybe about mass/massless particles. why does SM predict massless neutrinos, and 
%what implications does it have?
% \bibliographystyle{apalike}
% \bibliography{ref}
% \end{document}

### 2021-06-07 thesis/tex/nsiTheory.tex
update

% \begin{document}
\section{Non-standard interactions}
%TODO: moreintro. incompleteness of SM
Regarding the source of these new parameters, $\epsilon_{\ab}$ have the scale
\begin{align}
    \epsilon_{\ab} \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
\end{align} 
in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce NSI parameters in the order of $10^{-2}$, 
two magnitudes below the SM matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above TeV scale, 
we then predict that the NSI parameters contribute at most $10^{-2}$ to the SM matter effect, decreasing quadratically.

\subsection{Altering the Matter Potential}
Up until now, we have only considered neutrino interactions with electrons, protons, and neutrons. Now we extend this to include we can extend this to include 
the up and down quarks which are present in the Earth as the fundamental components of neutrons and protons. 
Consider interactions beyond the Standard Model through the following Lagrangians,
\begin{align*}
    \mathcal{L}_{\mathrm{CC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f f^{\prime} X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \ell_{\beta}\right)\left(\bar{f}^{\prime} \gamma_{\mu} P_{X} f\right) \\
    \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align*}
where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$.

We have no independent sensitivity for the neither chirality nor flavor type of $\epsilon^X$, so we sum over these and study the effective matter NSI parameter
 $\epsilon_{\ab}$:
\begin{align}
    \epsilon_{\ab} = \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \epsilon^{fX}_{\ab}\,.
\end{align}
Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
we get $N_u/N_e \simeq N_d/N_e \simeq 3$. Also we assume the components $\epsilon_{\a\b}$ to be real. Thus,
\begin{align}
    \epsilon_{\ab} =  \sum_X [\epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})]
\end{align}
Now, $\epsilon_{\ab}$ enters the Hamiltonian as entries of a potential-like matrix. In Eq.~\ref{eq:NSIH}, $A_{CC}\text{diag}(1,0,0)$ is our 
familiar matter potential from the Standard Model. There is also our new term, $A_{CC} \epsilon$, which contains the components $\epsilon_{\a\b}$:
\begin{align}\label{eq:NSIH}
    H &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}\text{diag}(1,0,0) + A_{CC} \epsilon \right] \nonumber \\
      &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}
      \begin{pmatrix}
          1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
          \epsilon_{\mu e} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
          \epsilon_{\tau e} & \epsilon_{\tau\mu} & \epsilon_{\tau\tau}
      \end{pmatrix} \right]\,.
\end{align} 
In the limit $\epsilon_{\ab} \to 0$, we recover the standard interaction Hamiltonian from Eq.~\ref{eq:H_3gen}.
We can draw several conclusions from this form of the Hamiltonian. Any nonzero off-diagonal element $\epsilon_{\ab}, \a \neq \b$ will make the NSI violate 
lepton flavor, just as the off-diagonal elements of $U$ does in the SM. Moreover, since the SM potential has the same order in $A_{CC}$ as the NSIs, 
any $\epsilon_{\ab} \sim 1$ will make the new matter effect be the same order as the SM effect.

We have two more modifications to the matrix $\epsilon$. First, all terms of the Hamiltonian must of course be Hermitian, thus
\begin{align}
    \begin{pmatrix}
        \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{\mu e} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
        \epsilon_{\tau e} & \epsilon_{\tau\mu} & \epsilon_{\tau\tau}
    \end{pmatrix} =
    \begin{pmatrix}
        \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{e \mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
    \end{pmatrix}\,.
\end{align}
Now we have reduced the possible number of NSI parameters from 9 down to 6. Moreover, it is common to subtract $\emm$ from the diagonal, which
we are free to do since any multiple added or subtracted from diagonal does not affect the eigenvectors of the Hamiltonian and thus not the
probabilities. So just as we subtracted away $V_{NC}$ back in Eq.~\ref{eq:components}, we can subtract $\emm$ and rotate it away.
Our NSI potential matrix now takes the form 
\begin{align}
    \begin{pmatrix}
        \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{e \mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
    \end{pmatrix} 
    - \epsilon_{\mu\mu}
    \begin{pmatrix}
        1 & 0 & 0 \\
        0 & 1 & 0 \\
        0 & 0 & 1 
    \end{pmatrix}
     &= \begin{pmatrix}
        \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau} - \epsilon_{\mu\mu}
    \end{pmatrix} \nonumber \\
    &= \begin{pmatrix}
        \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \ep
    \end{pmatrix}\,,
\end{align}
where $\ep = \ett - \emm$.

@@

Fig.~\ref{fig:Pee_eet_probs} shows the electron neutrino and antineutrino survival probabilities, and here we see
a clear difference when turning on $\eet$.
%TODO: clean up above and expand a bit.
\begin{figure}\label{fig:Pee_eet_probs}
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/Pee_eet_probs.pdf}
        \caption{Electron neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero.}
    \end{center}
\end{figure}

We summarize our findings in Table~\ref{table:nsi}
\begin{table}
    \begin{center}
    \begin{tabular}{lccc}
            \hline \hline & & \multicolumn{2}{c} {\text { Visibility }} \\
            \cline { 3 - 4 } \text {Parameter} & Range & \text { IC } & \text {DC } \\
            \hline
            $\ett$ &$\pm 0.05 $ & $\times$ & \checkmark \\
            $\emt$ &$\pm 0.02 $& \checkmark & \checkmark \\
            $\eem$ &$\pm 0.2 $& \checkmark & \checkmark \\
            $\eet$ &$\pm 0.2 $& $\times$ & \checkmark \\
            \hline
        \label{table:nsi}
    \end{tabular}
    \end{center}
    \caption{Table of NSI parameters and their ranges considered in this study, along with visibility off
    their signal in IceCube (IC) and DeepCore/PINGU (DC).}
\end{table}

>>>>

% \begin{document}
\section{Non-Standard Interactions}
We have already seen how the failure of the Standard Model to predict neutrino masses and flavor 
osillations forces us to amend it. We have no reason to believe that the Standard Model 
gauge group is the complete picture. Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
spontaneously broken to $U(1)_{EM}$, a higher order theory at a different energy scale with ompletely different
properties might be responsible for the Standard Model that we know. In this sense, the Standard Model might be considered 
an effective low energy theory, which is yiels impressive results in some areas, but failing in others. In fact, 
just as the fermion masses originate from the electroweak symmetry breaking, the neutrino masses might be generated from 
another broken symmetry resulting in the Standard Model gauge group.

%TODO: moreintro. incompleteness of SM
Following the discussion in~\cite{tommyNSI}, the new parameters $\epsilon$ have the scale
\begin{align}
    \epsilon \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
\end{align} 
in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce parameters in the order of $10^{-2}$, 
two magnitudes below the standard matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above electroweak scale, 
we then predict that the parameters contribute with at most a factor of $10^{-2}$ to the standard matter effect, decreasing quadratically.

\subsection{Altering the Matter Potential}
Up until now, we have only considered weak neutrino interactions with electrons, protons, and neutrons.
Following the approach of the Standard Model that the group generators uniquely determine the gauge bosons, a different gauge
theory will have different interactions than those we presently know. We call these interactions non-standard interactions (NSI).
We can phenomenologically allow these interactions to include the up and down quarks which are present 
in the Earth as the fundamental components of neutrons and protons, 
parametrized as model-independent four-fermion effective operators \cite{salvadoNSI,nsiFarzan}.
We write the Lagrangians
\begin{align*}
    \mathcal{L}_{\mathrm{CC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f f^{\prime} X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \ell_{\beta}\right)\left(\bar{f}^{\prime} \gamma_{\mu} P_{X} f\right) \\
    \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align*}
where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$. The CC NSI effect affects neutrino production and detection, and will not be considered here. NC NSI affect the matter potential, 
and is thus of interest to us.

We have no independent sensitivity for the neither chirality nor flavor type of $\epsilon^X$, so we sum over these and study the effective matter NSI parameter
 $\epsilon_{\ab}$:
\begin{align}
    \epsilon_{\ab} = \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \epsilon^{fX}_{\ab}\,.
\end{align}
Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
we get $N_u/N_e \simeq N_d/N_e \simeq 3$. Also we assume the components $\epsilon_{\a\b}$ to be real. Thus,
\begin{align}
    \epsilon_{\ab} =  \sum_X \epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})
\end{align}
Now, $\epsilon_{\ab}$ enters the Hamiltonian as entries of a potential-like matrix. In Eq.~\ref{eq:NSIH}, $A_{CC}\text{diag}(1,0,0)$ is our 
familiar matter potential from the Standard Model. There is also our new term, $A_{CC} \epsilon$, which contains the components $\epsilon_{\a\b}$:
\begin{align}\label{eq:NSIH}
    H &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}\text{diag}(1,0,0) + A_{CC} \epsilon \right] \nonumber \\
      &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}
      \begin{pmatrix}
          1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
          \epsilon_{\mu e} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
          \epsilon_{\tau e} & \epsilon_{\tau\mu} & \epsilon_{\tau\tau}
      \end{pmatrix} \right]\,.
\end{align} 
In the limit $\epsilon_{\ab} \to 0$, we recover the standard interaction Hamiltonian from Eq.~\ref{eq:H_3gen}.
We can draw several conclusions from this form of the Hamiltonian. Any nonzero off-diagonal element $\epsilon_{\ab}, \a \neq \b$ will make the NSI violate 
lepton flavor, just as the off-diagonal elements of $U$ does in the SM. Moreover, since the SM potential has the same order in $A_{CC}$ as the NSIs, 
any $\epsilon_{\ab} \sim 1$ will make the new matter effect be the same order as the SM effect.

We have two more modifications to the matrix $\epsilon$. First, all terms of the Hamiltonian must of course be Hermitian, thus
\begin{align}
    \begin{pmatrix}
        \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{\mu e} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
        \epsilon_{\tau e} & \epsilon_{\tau\mu} & \epsilon_{\tau\tau}
    \end{pmatrix} =
    \begin{pmatrix}
        \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
        \epsilon_{e \mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
        \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
    \end{pmatrix}\,.
\end{align}
Now we have reduced the possible number of NSI parameters from 9 down to 6.

% Moreover, it is common to subtract $\emm$ from the diagonal, which
% we are free to do since any multiple added or subtracted from diagonal does not affect the eigenvectors of the Hamiltonian and thus not the
% probabilities. So just as we subtracted away $V_{NC}$ back in Eq.~\ref{eq:components}, we can subtract $\emm$ and rotate it away.
% Our NSI potential matrix now takes the form 
% \begin{align}
%     \begin{pmatrix}
%         \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
%         \epsilon_{e \mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
%     \end{pmatrix} 
%     - \epsilon_{\mu\mu}
%     \begin{pmatrix}
%         1 & 0 & 0 \\
%         0 & 1 & 0 \\
%         0 & 0 & 1 
%     \end{pmatrix}
%      &= \begin{pmatrix}
%         \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
%         \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau} - \epsilon_{\mu\mu}
%     \end{pmatrix} \nonumber \\
%     &= \begin{pmatrix}
%         \epsilon_{ee}- \epsilon_{\mu\mu} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
%         \epsilon_{e \mu} & 0 & \epsilon_{\mu\tau}  \\
%         \epsilon_{e\tau} & \epsilon_{\mu\tau} & \ep
%     \end{pmatrix}\,,
% \end{align}
% where $\ep = \ett - \emm$.

@@

Fig.~\ref{fig:Pee_eet_probs} shows the electron neutrino and antineutrino survival probabilities, and here we see
a clear difference when turning on $\eet$.

We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
%TODO: clean up above and expand a bit.
\begin{figure}\label{fig:Pee_eet_probs}
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/Pee_eet_probs.pdf}
        \caption{Electron neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero.}
    \end{center}
\end{figure}

### 2021-06-07 thesis/tex/oscillations.tex
update

\input{commands}
\begin{document}

\section{Neutrino Mixing}\label{ch:oscillation}
%TODO: small intro about PMNS and justification of oscillations
\subsection{Mass Generation}
We consider a right-handed neutrino field, $\nu_R$. It has the usual properties of the conventional left-handed neutrino such as hypercharge and color zero. Moreover, since the electroweak gauge group $\text{SU}(2)_L$ only couple to left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the SM symmetry group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. This neutrino field is \emph{sterile} since it doesn't participate any of the SM interactions.

@@

\subsection*{The PMNS matrix}
Substituting the new transformation from Eq.~\ref{eq:nu_rotation} into the weak charged current, we get
\begin{align}\label{eq:j_CC2}
    j^\rho_L &= 2\bar{\nu}^\prime_{\alpha L} \gamma^\rho \ell_{\alpha L}^\prime \nonumber \\
             &= 2\bar{\nu}_{k L} V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} \gamma^\rho  \ell_{\alpha L}
\end{align}

@@

\subsection{Effective Matter Potentials}

@@

\subsection*{Matter oscillations}
Since only $\ne$ undergo CC interactions in Earth-like matter, the $V_{CC}$ potential is zero for all other flavors. However, since all flavors undergo NC interactions the total matter potential in matrix form is
\begin{align}\label{eq:V_matrix}
    V = \begin{bmatrix}
        V_{CC} + V_{NC} & 0 & 0 \\
        0 & V_{NC} & 0 \\
        0 & 0 & V_{NC} \\
    \end{bmatrix} = V_{CC}\, \delta_{\alpha e} + V_{NC}\,.
\end{align}
Just as in Eq.~\ref{eq:TDSE}, we start with a Hamiltonian that solves the time-dependent Schrödinger equation. This time, let the Hamiltonian be 
\begin{align}
    H = H_0 + H_{I}\,,
\end{align}
where $H_0$ is the Hamiltonian in vacuum, and $H_{I}$ is our interaction Hamiltonian associated with our matter potentials.
Let the wavefunction that describes the $\nu_\a \to \nu_\b$ transition be 
\begin{align}
    \bra{\nu_\b}\ket{\nu_\a (t)}\,,
\end{align}
i.e.~the evolution of the state of a neutrino emitted at $t =0$ with flavor $\alpha$ to flavor $\beta$ at time $t$.

>>>>

% \input{commands}
% \begin{document}

\section{Neutrino Mixing}\label{ch:oscillation}

%\subsection{Mass Generation}
In the Standard Model, fermion masses are generated by the Higgs mechanism through Yukawa couplings with the fermions right and left-handed components.
All neutrinos are left-handed and all antineutrinos are right-handed. Thus, neutrinos are massless since they do not undergo the Higgs mechanism.
Additionally, all terms of a Lagrangian that we construct must respect the gauge invariance. This removes the possibility of the neutrino mass to be 
generated at loop level because any such attempt will violate the total lepton number by two units.
In order to keep our theory renormalizable, we have one option left: introducing additional fermions.

We consider a right-handed neutrino field, $\nu_R$. Since the electroweak gauge group $\text{SU}(2)_L \times U(1)_Y$ only couple to 
left-handed particles and right-handed antiparticles, $\nu_R$ transforms as a singlet under the SM symmetry 
group $\mathrm{SU}(3)_{\mathrm{C}} \times \mathrm{SU}(2)_{L} \times \mathrm{U}(1)_{Y}$. 
This neutrino field is \emph{sterile} since it doesn't participate any of the SM interactions.

@@

\subsection{The mixing matrix}
Substituting the new transformation from Eq.~\ref{eq:nu_rotation} into the weak charged current, we get
\begin{align}\label{eq:j_CC2}
    j^\rho_L &= 2\bar{\nu}^\prime_{\alpha L} \gamma^\rho \ell_{\alpha L}^\prime \nonumber \\
             &= 2\bar{\nu}_{k L} V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} \gamma^\rho  \ell_{\alpha L}
\end{align}

@@

\subsection{Effective Potentials}

@@

\subsection{Matter Oscillations}
Since only $\ne$ undergo CC interactions in Earth-like matter, the $V_{CC}$ potential is zero for all other flavors. However, since all flavors undergo NC interactions the total matter potential in matrix form is
\begin{align}\label{eq:V_matrix}
    V = \begin{bmatrix}
        V_{CC} + V_{NC} & 0 & 0 \\
        0 & V_{NC} & 0 \\
        0 & 0 & V_{NC} \\
    \end{bmatrix} = V_{CC}\, \delta_{\alpha e} + V_{NC}\,.
\end{align}
Just as in Eq.~\ref{eq:TDSE}, we start with a Hamiltonian that solves the time-dependent Schrödinger equation. This time, let the Hamiltonian be 
\begin{align}
    H = H_0 + H_{I}\,,
\end{align}
where $H_0$ is the Hamiltonian in vacuum, and $H_{I}$ is our interaction Hamiltonian associated with our matter potentials.
Let the wavefunction that describes the $\nu_\a \to \nu_\b$ transition be 
\begin{align}
    \bra{\nu_\b}\ket{\nu_\a (t)}\,,
\end{align}
i.e.~the evolution of the state of a neutrino emitted at $t =0$ with flavor $\alpha$ to flavor $\beta$ at time $t$.
